An inventory of human light exposure related behaviour

### 2023-11-09 manuscript_SciRep.Rmd
Affiliation updated-MASJ

author:
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "1, 2,+"
    email         : "mushfiqul.anwarsiraji@monash.edu"
    role:
      - Formal Analysis
      - Visualization
      - Writing – original draft
      - Writing – review & editing

@@

  - name          : "Manuel Spitschan"
    corresponding : yes
    affiliation   : "11, 12, 13, *"
    email         : "manuel.spitschan@tum.de "
    role:
      - Conceptualization
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Methodology
      - Writing – original draft
      - Writing – review & editing

affiliation:
  - id            : "1"
    institution   : "Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
  - id            : "2"
    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
  - id            : "3"
    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
  - id            : "4"
    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
  - id            : "5"
    institution   : "Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands"
  - id            : "6"
    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands"
  - id            : "7"
    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia"
  - id            : "8"
    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
  - id            : "9"
    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"
  - id            : "10"
    institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
  - id            : "11"
    institution   : "TUM School of Medicine and Health, Technical University of Munich, Munich, Germany"
  - id            : "12"
    institution   : "TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany"
  - id            : "+"
    institution   : "Joint first author"

  - id            : "13"
    institution   : "North South University, Department of History and Philosophy, Bangladesh"

>>>>

author:
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "1, 2,+"
    email         : "mushfiqul.anwarsiraji@monash.edu"
    role:
      - Project administration
      - Methodology
      - Formal Analysis
      - Visualization
      - Writing – original draft
      - Writing – review & editing

@@

  - name          : "Manuel Spitschan"
    corresponding : yes
    affiliation   : "11, 12, 13, *"
    email         : "manuel.spitschan@tum.de "
    role:
      - Conceptualization
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Methodology
      - Writing – original draft
      - Writing – review & editing
      - Supervision

affiliation:
  - id            : "1"
    institution   : "Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
  - id            : "2"
    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"

  - id            : "3"
    institution   : "North South University, Department of History and Philosophy, Bangladesh"

  - id            : "4"
    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
  - id            : "5"
    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
  - id            : "6"
    institution   : "Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands"
  - id            : "7"
    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands"
  - id            : "8"
    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia"
  - id            : "9"
    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
  - id            : "10"
    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"
  - id            : "11"
    institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
  - id            : "12"
    institution   : "TUM School of Medicine and Health, Technical University of Munich, Munich, Germany"
  - id            : "13"
    institution   : "TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany"
  - id            : "+"
    institution   : "Joint first author"

### 2023-11-09 manuscript_SciRep.tex
Affiliation updated-MASJ

The authors made the following contributions. Mushfiqul Anwar Siraji: Formal Analysis, Visualization, Writing -- original draft, Writing -- review \& editing; Rafael Robert Lazar: Data curation, Investigation, Project administration, Visualization, Writing -- original draft, Writing -- review \& editing; Juliëtte van Duijnhoven: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Luc Schlangen: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Shamsul Haque: Conceptualization, Supervision, Writing -- review \& editing; Vineetha Kalavally: Supervision, Writing -- review \& editing; Céline Vetter: Conceptualization, Writing -- review \& editing; Gena Glickman: Conceptualization, Methodology, Writing -- review \& editing; Karin Smolders: Conceptualization, Methodology, Writing -- review \& editing; Manuel Spitschan: Conceptualization, Data curation, Investigation, Project administration, Visualization, Methodology, Writing -- original draft, Writing -- review \& editing.

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia\\\textsuperscript{2} Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland\\\textsuperscript{3} University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland\\\textsuperscript{4} Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands\\\textsuperscript{5} Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands\\\textsuperscript{6} Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands\\\textsuperscript{7} Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia\\\textsuperscript{8} University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA\\\textsuperscript{9} Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA\\\textsuperscript{10} Translational Sensory \& Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany\\\textsuperscript{11} TUM School of Medicine and Health, Technical University of Munich, Munich, Germany\\\textsuperscript{12} TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany\\\textsuperscript{*} Joint first author\\\textsuperscript{13} North South University, Department of History and Philosophy, Bangladesh\\\textsuperscript{+} Co First Author\\\textsuperscript{*} Corresponding Author}

>>>>

The authors made the following contributions. Mushfiqul Anwar Siraji: Project administration, Methodology, Formal Analysis, Visualization, Writing -- original draft, Writing -- review \& editing; Rafael Robert Lazar: Data curation, Investigation, Project administration, Visualization, Writing -- original draft, Writing -- review \& editing; Juliëtte van Duijnhoven: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Luc Schlangen: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Shamsul Haque: Conceptualization, Supervision, Writing -- review \& editing; Vineetha Kalavally: Supervision, Writing -- review \& editing; Céline Vetter: Conceptualization, Writing -- review \& editing; Gena Glickman: Conceptualization, Methodology, Writing -- review \& editing; Karin Smolders: Conceptualization, Methodology, Writing -- review \& editing; Manuel Spitschan: Conceptualization, Data curation, Investigation, Project administration, Visualization, Methodology, Writing -- original draft, Writing -- review \& editing, Supervision.

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia\\\textsuperscript{2} Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland\\\textsuperscript{3} North South University, Department of History and Philosophy, Bangladesh\\\textsuperscript{4} University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland\\\textsuperscript{5} Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands\\\textsuperscript{6} Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands\\\textsuperscript{7} Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands\\\textsuperscript{8} Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia\\\textsuperscript{9} University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA\\\textsuperscript{10} Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA\\\textsuperscript{11} Translational Sensory \& Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany\\\textsuperscript{12} TUM School of Medicine and Health, Technical University of Munich, Munich, Germany\\\textsuperscript{13} TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany\\\textsuperscript{+} Joint first author\\\textsuperscript{*} Corresponding Author}
